### 2016-01-18 paper.tex
Add 'The'

The effect of Reynolds number on average power output was shown to be
significant on the 2 m Sandia Research Darrieus turbine in wind tunnel testing
\cite{Blackwell1976}: Maximum power coefficient, $C_{P_{\max}}$, increased with
Reynolds number, $Re_c$ (based on blade chord rather than diameter, though these
are approximately proportional), along with a shift of the location of
$C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
effects of Reynolds number were quite dramatic over a relatively small range of
$Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that performance and
near-wake characteristics of a high solidity cross-flow turbine become Reynolds
number independent at $Re_c \approx 2 \times 10^5$.

>>>>

The effect of Reynolds number on average power output was shown to be
significant on the 2 m Sandia Research Darrieus turbine in wind tunnel testing
\cite{Blackwell1976}: The maximum power coefficient, $C_{P_{\max}}$, increased
with Reynolds number, $Re_c$ (based on blade chord rather than diameter, though
these are approximately proportional), along with a shift of the location of
$C_{P_{\max}}$ toward lower tip speed ratios due to delayed blade stall. The
effects of Reynolds number were quite dramatic over a relatively small range of
$Re_c \approx 1.1 \times 10^5$--$2.9 \times 10^5$. More recently, Bachant and
Wosnik \cite{Bachant2014, Bachant2015-RVAT-Re-dep} showed that performance and
near-wake characteristics of a high solidity cross-flow turbine become Reynolds
number independent at $Re_c \approx 2 \times 10^5$.
